Basic Bibliography and Reference Testing

### 2022-04-15 _support/reference/biblatex_basic/biblatex_test.tex
ref: Working paper biblatex formats; display url if no doi

\usepackage[colorlinks=true, linkcolor=blue, citecolor=blue, plainpages=false, pdfpagelabels=true, urlcolor=blue]{hyperref}
\usepackage[bottom]{footmisc}

\usepackage{filecontents}
% This creates a bib file called ref.bib in the same folder as the current tex file
\begin{filecontents}{ref.bib}
@article{becker_human_1986,
	title = {Human Capital and the Rise and Fall of Families},
	volume = {4},
	url = {http://ideas.repec.org/a/ucp/jlabec/v4y1986i3ps1-39.html},
	pages = {S1--39},
	number = {3},
	journaltitle = {Journal of Labor Economics},
	author = {Becker, Gary S and Tomes, Nigel},
	urldate = {2012-02-15},
	date = {1986}
}
@article{case_lasting_2005,
	title = {The lasting impact of childhood health and circumstance},
	volume = {24},
	issn = {0167-6296},
	url = {http://www.ncbi.nlm.nih.gov/pubmed/15721050},
	doi = {10.1016/j.jhealeco.2004.09.008},
	pages = {365--389},
	number = {2},
	journaltitle = {Journal of health economics},
	shortjournal = {J Health Econ},
	author = {Case, Anne and Fertig, Angela and Paxson, Christina},
	urldate = {2012-06-13},
	date = {2005-03},
	pmid = {15721050},
	keywords = {Adult, child, Child Welfare, Cohort Studies, Great Britain, Health Status Indicators, Humans, Social Class}
}
@article{conti_understanding_2010,
	title = {Understanding the Early Origins of the Education–Health Gradient},
	volume = {5},
	issn = {1745-6916, 1745-6924},
	url = {http://pps.sagepub.com/content/5/5/585.abstract},
	doi = {10.1177/1745691610383502},
	pages = {585--605},
	number = {5},
	journaltitle = {Perspectives on Psychological Science},
	author = {Conti, Gabriella and Heckman, James J},
	urldate = {2012-02-16},
	date = {2010-09-01},
	keywords = {health, education, genetics, treatment effects}
}
\end{filecontents}

\usepackage[authordate,
backend=bibtex,
doi=false,
isbn=false,
sorting=nyt,
maxbibnames=10,
maxcitenames=3,
sortcites=False]{biblatex-chicago}
\bibliography{ref}

@@

\paragraph{\href{https://papers.ssrn.com/sol3/papers.cfm?abstract_id=3140132}{Data}}

@@

\pagebreak
\begingroup
%\setstretch{1.1}
\setlength\bibitemsep{0pt}
\printbibliography
\endgroup
\pagebreak

>>>>

\usepackage[colorlinks=true, linkcolor=blue, citecolor=blue, plainpages=false, pdfpagelabels=true, urlcolor=blue]{hyperref}
\usepackage[bottom]{footmisc}
% setspace: for spacing gap in references
\usepackage{setspace}

\usepackage[
  authordate,
  backend=biber,
  isbn=false,
  sorting=nyt,
  maxbibnames=10,
  maxcitenames=3,
  sortcites=true]{biblatex-chicago}

\usepackage{filecontents}
% This creates a bib file called ref.bib in the same folder as the current tex file
\begin{filecontents}{ref.bib}
@book{becker_human_1994,
  title = {Human {{Capital}}: {{A Theoretical}} and {{Empirical Analysis}}, with {{Special Reference}} to {{Education}}, 3rd {{Edition}}},
  author = {Becker, Gary S.},
  date = {1994-03-14},
  edition = {3rd edition},
  publisher = {{University of Chicago Press}},
  location = {{Chicago}},
  isbn = {978-0-226-04120-9},
  pagetotal = {412}
}
@article{becker_human_1986,
	title = {Human Capital and the Rise and Fall of Families},
	volume = {4},
	url = {http://ideas.repec.org/a/ucp/jlabec/v4y1986i3ps1-39.html},
	pages = {S1--39},
	number = {3},
	journaltitle = {Journal of Labor Economics},
	author = {Becker, Gary S and Tomes, Nigel},
	urldate = {2012-02-15},
	date = {1986}
}
@article{case_lasting_2005,
	title = {The lasting impact of childhood health and circumstance},
	volume = {24},
	issn = {0167-6296},
	url = {http://www.ncbi.nlm.nih.gov/pubmed/15721050},
	doi = {10.1016/j.jhealeco.2004.09.008},
	pages = {365--389},
	number = {2},
	journaltitle = {Journal of health economics},
	shortjournal = {J Health Econ},
	author = {Case, Anne and Fertig, Angela and Paxson, Christina},
	urldate = {2012-06-13},
	date = {2005-03},
	pmid = {15721050},
	keywords = {Adult, child, Child Welfare, Cohort Studies, Great Britain, Health Status Indicators, Humans, Social Class}
}
@article{conti_understanding_2010,
	title = {Understanding the Early Origins of the Education–Health Gradient},
	volume = {5},
	issn = {1745-6916, 1745-6924},
	url = {http://pps.sagepub.com/content/5/5/585.abstract},
	doi = {10.1177/1745691610383502},
	pages = {585--605},
	number = {5},
	journaltitle = {Perspectives on Psychological Science},
	author = {Conti, Gabriella and Heckman, James J},
	urldate = {2012-02-16},
	date = {2010-09-01},
	keywords = {health, education, genetics, treatment effects}
}
@article{hao_air_2016,
	title = {Air {Pollution} and {Preterm} {Birth} in the {U}.{S}. {State} of {Georgia} (2002–2006): {Associations} with {Concentrations} of 11 {Ambient} {Air} {Pollutants} {Estimated} by {Combining} {Community} {Multiscale} {Air} {Quality} {Model} ({CMAQ}) {Simulations} with {Stationary} {Monitor} {Measurements}},
	volume = {124},
	issn = {0091-6765, 1552-9924},
	shorttitle = {Air {Pollution} and {Preterm} {Birth} in the {U}.{S}. {State} of {Georgia} (2002–2006)},
	url = {https://ehp.niehs.nih.gov/doi/10.1289/ehp.1409651},
	doi = {10.1289/ehp.1409651},
	language = {en},
	number = {6},
	urldate = {2020-07-18},
	journal = {Environmental Health Perspectives},
	author = {Hao, Hua and Chang, Howard H. and Holmes, Heather A. and Mulholland, James A. and Klein, Mitch and Darrow, Lyndsey A. and Strickland, Matthew J.},
	month = jun,
	year = {2016},
	pages = {875--880}
}
@article{westergaard_ambient_2017,
	title = {Ambient air pollution and low birth weight - are some women more vulnerable than others?},
	volume = {104},
	issn = {01604120},
	url = {https://linkinghub.elsevier.com/retrieve/pii/S0160412017301976},
	doi = {10.1016/j.envint.2017.03.026},
	language = {en},
	urldate = {2020-07-19},
	journal = {Environment International},
	author = {Westergaard, Nadja and Gehring, Ulrike and Slama, Rémy and Pedersen, Marie},
	month = jul,
	year = {2017},
	pages = {146--154},
}
@report{cavounidis_2022,
  title = {Estimating the Nature of Technological Change:
    Exploiting Shifts in Skill Use Within and Between Occupations},
  author = {Cavounidis, Costas and
    Dicandia, Vittoria and
    Lang, Kevin and
    Malhotra, Raghav},
  date = {2022},
  institution = {Mimeo,
    Department of Economics,
    Univerity of Warwick}
}
@report{morchio_moser_2021,
  title = {The Gender Pay Gap: Micro Sources and Macro Consequences},
  author = {Morchio, Iacopo and Moser, Christian},
  date = {2021},
  series = {CEPR Discussion Papers},
  number = {15283},
  url = {https://ideas.repec.org/p/cpr/ceprdp/16383.html}
}
\end{filecontents}

% https://tex.stackexchange.com/a/424775/109818
\DeclareSourcemap{
  \maps[datatype=bibtex]{
    \map[overwrite]{
      \step[fieldsource=doi, final]
      \step[fieldset=url, null]
      \step[fieldset=eprint, null]
    }
  }
}
\addbibresource{ref.bib}

@@

\section{biblatex Settings}

\subsection{Chicago Author-Date}

To use authordate chicago stye, cite up to three authors in text, more than three authors use `et al.', and cite in the references at most ten author names.

\begin{verbatim}
  \usepackage[
    authordate,
    backend=biber,
    isbn=false,
    sorting=nyt,
    maxbibnames=10,
    maxcitenames=3,
    sortcites=true]{biblatex-chicago}
\end{verbatim}

\subsection{DOI or URL if DOI does not Exist}

Using \textbf{biber} as backend, can use the `sourcemap' feature to control: (1) print doi if exists; (2) print url if doi does not exist; (3) print eprint if no doi and also no url. See \url{https://tex.stackexchange.com/a/424799/109818}.

\begin{verbatim}
\DeclareSourcemap{
  \maps[datatype=bibtex]{
    \map[overwrite]{
      \step[fieldsource=doi, final]
      \step[fieldset=url, null]
      \step[fieldset=eprint, null]
    }
  }
}
\end{verbatim}

\section{Citations}
\subsection{Possessive Citations}

In this example, using possessive to put apostrophe after author names and before date. Accomplished by using \emph{citeauthor} first then \emph{parentcite}.

\citeauthor{hao_air_2016}'s \parencite*{hao_air_2016} Georgia study
found that associations of traffic-related pollutants, including NO\textsubscript{2} and
PM\textsubscript{2.5}, with preterm birth tended to be stronger for mothers with low
educational attainment.

\subsection{Cite Only Date}

To write more flexibly, can mention author names explicitly in text and then cite the article with \emph{parentcite} for the date only: Westergaard and her colleagues \parencite*{westergaard_ambient_2017} identified only a small handful of studies that addressed effect modification by dimensions of socioeconomic status.

\subsection{Full Article Title In-Text Citation}

To cite the entire title of the the paper, we can use \emph{citetitle}: The article, \citetitle{conti_understanding_2010}, by \citeauthor{conti_understanding_2010}, published in year \cite*{conti_understanding_2010}, is been discussed in this sentence.

We can also cite the full title of a book or an article, rather then using \emph{textcite}, we use \emph{citetitle} first, followed by \emph{autocite}:
\begin{itemize}
    \item \citetitle{conti_understanding_2010} \autocite{conti_understanding_2010} is an article published in a journal.
    \item \citetitle{becker_human_1994} \autocite{becker_human_1994} is a book we are reading today.
\end{itemize}

\section{BIB Entries}

\subsection{BIB Entry for non-public Working Paper}

For working papers that have not been shared on public repositories. Here we cite \textcite{cavounidis_2022}.

\begin{verbatim}
  @report{cavounidis_2022,
    title = {Estimating the Nature of Technological Change:
      Exploiting Shifts in Skill Use Within and Between Occupations},
    author = {Cavounidis, Costas and
      Dicandia, Vittoria and
      Lang, Kevin and
      Malhotra, Raghav},
    date = {2022},
    institution = {Mimeo,
      Department of Economics,
      Univerity of Warwick}
  }
\end{verbatim}

\subsection{BIB Entry for Working Paper in Series}

For working paper in various working paper series. \textcite{morchio_moser_2021} is a CEPR Discussion Paper.

\begin{verbatim}
@report{morchio_moser_2021,
  title = {The Gender Pay Gap: Micro Sources and Macro Consequences},
  author = {Morchio, Iacopo and Moser, Christian},
  date = {2021},
  series = {CEPR Discussion Papers},
  number = {15283},
  url = {https://ideas.repec.org/p/cpr/ceprdp/16383.html}
}
\end{verbatim}

\section{\href{https://papers.ssrn.com/sol3/papers.cfm?abstract_id=3140132}{Data}}

@@

\pagebreak
\begingroup
\setstretch{1.0}
\setlength\bibitemsep{3pt}
\printbibliography
\endgroup
\pagebreak
